%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
  {Senior Full Stack Engineer} % Job title
  {BrainFx Inc.} % Organization
  {Sep. 2020 - Current} % Location
  {(remote) Pickering, Ontario, CA} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Planned, developed and implemented security for end-user and server-to-server \importantstyle{authentication} and \importantstyle{authorization}:}
        \begin{cvsubitems}
          \item {Leveraged asymmetric \importantstyle{cryptography} to ensure data \importantstyle{integrity}.}
          \item {Integrated with \importantstyle{Drupal}, \importantstyle{NestJS} and \importantstyle{NuxtJS} through architecting new custom native components.}
          \item {Made server-to-server calls on behalf of end-users possible.}
        \end{cvsubitems}
      \item {Gathered requirements and planned to deprecate the existing legacy platforms and incrementally replacing them with an API built upon Drupal:}
        \begin{cvsubitems}
          \item {Refactored the legacy platforms' databases to support new features}.
          \item {Updated the Drupal \importantstyle{back-end} and \importantstyle{UI} with new business requirements for the increased diversity of customers}.
          \item {Designed and implemented the new subscription-based model and completed the pay-per-use removal}.
        \end{cvsubitems}
      \item {Architected and implemented a new sub-platform back-end application according to the \importantstyle{DDD} architectural pattern:}
        \begin{cvsubitems}
          \item {Initialized the \importantstyle{RESTful} and \importantstyle{Websockets} API, \importantstyle{Data Access Layer} (Repository Pattern for \importantstyle{MongoDB}), internal modules structures and their intercommunication patterns (\importantstyle{asynchronous}, \importantstyle{event-driven})}.
          \item {Implemented the new sub-platform using \importantstyle{NestJS}, \importantstyle{TypeScript}, \importantstyle{Mongoose}}.
        \end{cvsubitems}
        \item {Implemented \importantstyle{PWA Service Workers}' update workflow via \importantstyle{VueJS}, \importantstyle{NuxtJS} and Workbox}.
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {York University} % Organization
    {Computer Security Research Assistant} % Job title
    {Jan. 2020 - Aug. 2020} % Date(s)
    {North York, Ontario, CA} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Malwareless Web Analytics Pollution Tools Analysis and Development:}
          \begin{cvsubitems}
            \item {Evaluated overall feasibility and effectiveness of conducting successful malwareless attacks.}
            \item {Developed new \importantstyle{multithreaded MWAP attack tool} (\underline{\href{https://github.com/saaniaki/eloki}{github.com/saaniaki/eloki}}) in \importantstyle{Java} and \importantstyle{Maven} using HtmlUnit and Selenium to precisely assess \importantstyle{Google Analytics} and \importantstyle{AWStats} vulnerabilities to fake requests and successfully manipulate analytical data.}
            \item {Developed a feature to bypass known bot-detecting tools (\importantstyle{Google reCAPTCHA v3}).}
          \end{cvsubitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Tread2Go Inc.} % Organization
    {Co-founder \& CTO} % Job title
    {Jun. 2019 - Jun. 2020} % Date(s)
    {Richmond Hill, Ontario, CA} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\importantstyle{Architected} and developed a mini ERP \importantstyle{REST API} using \importantstyle{Spring Boot}, \importantstyle{Spring Cloud} and deployed on \importantstyle{AWS} Beanstalk:}
          \begin{cvsubitems}
            \item {Highly \importantstyle{scalable} and convertible to \importantstyle{microservices}.}
            \item {Significantly \importantstyle{improved performance (80\%)} by automatically scheduling orders, managing resources and optimizing operations.}
            \item {Integrated and used various third-party APIs to make the development process faster  (Firebase, Google Cloud APIs, Nexmo, Stripe and more).}
            \item {Applied best practices and design patterns to develop RBAC using \importantstyle{Spring Security}.}
          \end{cvsubitems}
        \item {Initiated Tread2Go \importantstyle{Angular PWA} and managed \importantstyle{Angular} front-end team using Trello, GitHub and Swagger; improved \importantstyle{interpersonal skills} to lead the project and \importantstyle{soft skills} to manage the stressful environment:}
          \begin{cvsubitems}
            \item {Repetitively converted business requirements to practical development plans, managed and executed development plans using the \importantstyle{defined budget}, enabled the company to continue working with \importantstyle{lean} and \importantstyle{agile} strategy.}
          \end{cvsubitems}
        \item {Deployed and maintained PWA and server-side services, orchestrated DNS, Security Policies, S3, EC2, Beanstalk, RDS and SES:}
          \begin{cvsubitems}
            \item {Applied and set up \importantstyle{DevOps} using Amplify and GitHub to \importantstyle{ease PWA delivery} significantly.}
          \end{cvsubitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Scotiabank} % Organization
    {Information Security Analyst} % Job title
    {Jan. 2019 - Apr. 2019} % Date(s)
    {Scarborough, Ontario, CA} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a \importantstyle{robust cryptography} tool in Java without using any frameworks (security requirement) to include the least number of external libraries:}
          \begin{cvsubitems}
            \item {Compatible with \importantstyle{OpenSSL} standards; leverages from both \importantstyle{Symmetric} and \importantstyle{Asymmetric} cryptography; \importantstyle{digitally signs} documents.}
          \end{cvsubitems}
        \item {Analyzed application security (SAST \& DAST) using Micro Focus Fortify, WebInspect and Blackduck.}
        \item {Integrated new security analysis and management software using \importantstyle{Python 3} to make analyzing static source code vulnerabilities \importantstyle{more efficient} and \importantstyle{automated}:}
          \begin{cvsubitems}
            \item {Utilized Jira, Bitbucket and \importantstyle{Jenkins} to improve application delivery process.}
          \end{cvsubitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {CubeAngle Inc.} % Organization
    {Full Stack Developer} % Job title
    {Jul. 2018 - Sep. 2018} % Date(s)
    {Markham, Ontario, CA} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\importantstyle{Architected} and developed Trade Dimension Dashboard using \importantstyle{Angular} and \importantstyle{Spring Boot} frameworks (\importantstyle{REST API}):}
          \begin{cvsubitems}
            \item {\importantstyle{Cloud-based} web application to visualize trade data stored on \importantstyle{AWS} Redshift.}
          \end{cvsubitems}
        \item {Utilized cloud computing concepts and various \importantstyle{AWS} tools for deployment (\importantstyle{Cognito}, \importantstyle{RDS}, \importantstyle{API Gateway}, \importantstyle{Ubuntu EC2}, \importantstyle{Amplify}).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Vaster Inc.} % Organization
    {Web Application Developer} % Job title
    {Apr. 2017 - May. 2018} % Date(s)
    {North York, Ontario, CA} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed Vaster Dashboard using \importantstyle{Angular} and Symfony (\importantstyle{REST API}) to visualize data and support CRUD operations, deployed on CentOS EC2.}
        \item {\importantstyle{Architected} and developed \importantstyle{Cloud-based} API of Novo Chat by adapting \importantstyle{Spring Boot}, \importantstyle{Spring Cloud} and \importantstyle{Docker}:}
          \begin{cvsubitems}
            \item {Implemented Discovery Service, Default Gateway, Configuration server and other \importantstyle{microservices}, deployed on multiple Ubuntu EC2 instances.}
          \end{cvsubitems}
        \item {Applied \importantstyle{best security practices} for authentication and \importantstyle{microservices} secure communication (JWT).}
      \end{cvitems}
      % \begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      % \end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
